TODO: A Survey of StarCraft AI Techniques

### 2012-05-14 survey.tex
Incorporated AIUR in the paper

Figure \ref{fig:bot-architecture} shows some representative examples of the integration architectures used by different bots in the AIIDE and CIG 2011 Starcraft AI competitions \cite{url1,url2}: BroodwarQ \cite{???}, Nova \cite{???}, UAlbertaBot \cite{???}, Skynet \cite{???}, SPAR \cite{???}, and BTHAI \cite{???} (see Section \ref{sec:competition} for a comparison of their performance). Each box represents an individual module with a clearly defined task (only modules with a black background can send actions directly to Starcraft). Dashed arrows represent data flow, and solid arrows represent control (when a module can command another module to perform some task). For example, we can see how SPAR is divided in two sets of modules: {\em situation analysis} and {\em decision making}, the first with three modules dedicated to analyze the current situation of the game, and the later with 4 modules dedicated to exploit that information to decide what to do. We can see how the decision making aspect of SPAR is organized hierarchically, with the higher-level module ({\em strategic decision}) issuing commands to the next module ({\em tactical decision}), which sends commands to the next module ({\em action implementation}), and so on. Only the lower-level modules can send actions directly to Starcraft.

@@

\begin{itemize}
\item BroodwarBotQ: uses abstraction for micro-management, and divide-and-conquer for macro-management and intelligence gathering. To avoid conflicts between modules (since the individual tasks of each of the modules are not completely independent), BBQ uses an arbitrator.
\item Nova: is similar in design as BroodwarBotQ, and uses abstraction for micro-management, and divide-and-conquer for macro-management. The differences are that Nova does not have an arbitrator to resolve conflicts, but has a higher-level module ({\em strategy manager}), which posts information to the blackboard that the rest of modules follow (thus, making use of abstraction).
\item UAlbertaBot: also uses abstraction in micro-management like the previous two bots. But it also uses it in macro-management: as can be seen, the production manager sends commands to the building manager, who is in charge of producing the buildings. This bot also uses divide-and-conquer, and tasks like scouting and resource gathering are managed by separate, independent modules.
\item Skynet: makes extensive use of both abstraction and divide-and-conquer. Considering the decision making component of Skynet, we can see a high level module that issues commands to a series of tactics modules. The collection of tactic modules queue {\em tasks} (that are analogous to the abstract actions used in SPAR). Each different task has a specific low level module that knows how to execute it. Thus, Skynet uses a 3 layered abstraction hierarchy, and uses divide-and-conquer in all levels except the highest.
\item SPAR: only uses abstraction. Its high-level module determines the strategy to use, and the tactical decision module divides it into a collection of {\em abstract actions}, that are executed by the lower-level modules.
\item BTHAI: uses a two-tier abstraction hierarchy, where a collection of high-level modules command a collection of lower-level agents in charge of each of the units. At the high-level, BTHAI uses divide-and-conquer, having multiple high-level modules issuing commands to the lower-level units.
\end{itemize}

@@

Most bots using divide-and-conquer (except for BBQ and UAlbertaBot), assume that each of the modules can act independently and that their actions can be executed without interference. BBQ and UAlbertaBot use an arbitrator ({\em Game Commander'} in UAlbertaBot) that makes sure that modules do not send contradictory orders to the same unit. However, very little bots handle the problem of how to coordinate resource usage amongst modules, for instance BTHAI uses a first-come-first-serve policy for spending resources, the first module that requests resources is the one that gets them. Nova and Skynet are exceptions, and implement some rudimentary prioritization based on the high level strategy.

One interesting aspect of the five bots described above is that, while all of them are reactive at the lower level (unit control), most if not all of them, are scripted at the highest level of abstraction. BTHAI reads build and squad formations from a predefined script, Nova's {\em Strategy Manager} is a predefined finite-state machine, BBQ's construction manager reads the build order from a predefined script, and Skynet's {\em BuildOrder Manager} is basically a predefined script. Such scripts describe the strategy that the bots will use, however, such strategy is always fixed. One could see this pre-scripting as if each bot defined a ``high-level programming language'' to describe Starcraft strategies, and the bots themselves are just interpreters of such strategy. Compared to current approaches for Chess or Go, this scripting seems a rigid and inflexible, but responds to the much higher complexity of the Starcraft game. An interesting exception to that is UAlbertaBot, which uses a search algorithm in the {\em Production Manager} to find near-optimal build orders.

>>>>

Figure \ref{fig:bot-architecture} shows some representative examples of the integration architectures used by different bots in the AIIDE and CIG 2011 Starcraft AI competitions \cite{url1,url2}: BroodwarQ \cite{???}, Nova \cite{???}, UAlbertaBot \cite{???}, Skynet \cite{???}, SPAR \cite{???}, AIUR \cite{???}, and BTHAI \cite{???} (see Section \ref{sec:competition} for a comparison of their performance). Each box represents an individual module with a clearly defined task (only modules with a black background can send actions directly to Starcraft). Dashed arrows represent data flow, and solid arrows represent control (when a module can command another module to perform some task). For example, we can see how SPAR is divided in two sets of modules: {\em situation analysis} and {\em decision making}, the first with three modules dedicated to analyze the current situation of the game, and the later with 4 modules dedicated to exploit that information to decide what to do. We can see how the decision making aspect of SPAR is organized hierarchically, with the higher-level module ({\em strategic decision}) issuing commands to the next module ({\em tactical decision}), which sends commands to the next module ({\em action implementation}), and so on. Only the lower-level modules can send actions directly to Starcraft.

@@

\begin{itemize}
\item BroodwarBotQ: uses abstraction for micro-management, and divide-and-conquer for macro-management and intelligence gathering. To avoid conflicts between modules (since the individual tasks of each of the modules are not completely independent), BBQ uses an arbitrator.
\item Nova: is similar in design as BroodwarBotQ, and uses abstraction for micro-management, and divide-and-conquer for macro-management. The differences are that Nova does not have an arbitrator to resolve conflicts, but has a higher-level module ({\em strategy manager}), which posts information to the blackboard that the rest of modules follow (thus, making use of abstraction).
\item UAlbertaBot: also uses abstraction in micro-management like the previous two bots. But it also uses it in macro-management: as can be seen, the production manager sends commands to the building manager, who is in charge of producing the buildings. This bot also uses divide-and-conquer, and tasks like scouting and resource gathering are managed by separate, independent modules.
\item Skynet: makes extensive use of both abstraction and divide-and-conquer. Considering the decision making component of Skynet, we can see a high level module that issues commands to a series of tactics modules. The collection of tactic modules queue {\em tasks} (that are analogous to the abstract actions used in SPAR). Each different task has a specific low level module that knows how to execute it. Thus, Skynet uses a 3 layered abstraction hierarchy, and uses divide-and-conquer in all levels except the highest.
\item SPAR: only uses abstraction. Its high-level module determines the strategy to use, and the tactical decision module divides it into a collection of {\em abstract actions}, that are executed by the lower-level modules.
\item AIUR: is mainly divide-and-conquer oriented, for macro as well as for micro, with a slight abstraction on macro with a SpendManager deciding how to spend resources among Base, Production and Construction Managers. At the beginning of a game, the MoodManager initializes a ``mood'' which will influence both micro and macro. For example, micro-management is divided into three independent managers: the {\em Defense Manager}, controlling military units when there is nothing special, the {\em Under Attack Manager}, activated when the opponent is attacking our bases, and the {\em Army Manager}, taking control of units when it is time to attack, following a timing given by the current mood.
\item BTHAI: uses a two-tier abstraction hierarchy, where a collection of high-level modules command a collection of lower-level agents in charge of each of the units. At the high-level, BTHAI uses divide-and-conquer, having multiple high-level modules issuing commands to the lower-level units.
\end{itemize}

@@

Some bots using divide-and-conquer, assume that each of the modules can act independently and that their actions can be executed without interference. BBQ, UAlbertaBot and AIUR, however use an arbitrator ({\em Game Commander'} in UAlbertaBot) that makes sure that modules do not send contradictory orders to the same unit. However, very little bots handle the problem of how to coordinate resource usage amongst modules, for instance BTHAI uses a first-come-first-serve policy for spending resources, the first module that requests resources is the one that gets them. Nova and Skynet are exceptions, and implement some rudimentary prioritization based on the high level strategy. Following available resources and timing, AIUR's {\em Spend Manager} orders Base, Production and Construction Managers what they have to build/produce. It also orders to start tech research and upgrades.

One interesting aspect of the five bots described above is that, while all of them are reactive at the lower level (unit control), most if not all of them, are scripted at the highest level of abstraction. BTHAI reads build and squad formations from a predefined script, Nova's {\em Strategy Manager} is a predefined finite-state machine, BBQ's construction manager reads the build order from a predefined script, and Skynet's {\em BuildOrder Manager} is basically a predefined script. Such scripts describe the strategy that the bots will use, however, such strategy is always fixed. One could see this pre-scripting as if each bot defined a ``high-level programming language'' to describe Starcraft strategies, and the bots themselves are just interpreters of such strategy. Compared to current approaches for Chess or Go, this scripting seems a rigid and inflexible, but responds to the much higher complexity of the Starcraft game. An interesting exception to that is UAlbertaBot, which uses a search algorithm in the {\em Production Manager} to find near-optimal build orders. Another interesting case is AIUR, that uses a {\em Mood Manager} to randomly pick a mood among five (rush, aggressive, defensive, macro, fast expand), which will influence the build order, strategy and tactics, all of them scripted so far. This mood can change during the game, following the opponent behavior.
